Canonical rings of log spin stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
\sx with floored divisor -> \sx no floor divisor
title change, bold group in Fuchsian group

\title{Spin canonical rings of log stacky curves}

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, i.e.,~ a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to desribe the ring $M(\Gamma),$ is to write down a presentation.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

@@

By the Generalized Max Noether Theorem for genus 0 curves (see Voight
and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
\begin{align}
\label{eqn:noether-377}
	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(k - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	k \halfcan' \rfloor)
\end{align}

@@

\begin{align*}
	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(k - 3) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
	k \halfcan' \rfloor) \text{ if } k \geq 12 \text{ and } 3 \nmid k \\
	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(k - 7) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
	k \halfcan' \rfloor) \text{ if } k \geq 6, k \not\equiv 0, 5
	\bmod 7
\end{align*}

>>>>

\title{Canonical rings of log spin stacky curves}

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian group}, i.e.,~ a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma),$ is to write down a presentation.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

@@

By the Generalized Max Noether Theorem for genus 0 curves (see Voight
and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
\begin{align}
\label{eqn:noether-377}
	H^0 (\sx', 21 \cdot \halfcan') \otimes H^0 (\sx',
	(k - 21) \halfcan') \rightarrow H^0 (\sx',
	k \halfcan')
\end{align}

@@

\begin{align*}
	&H^0 (\sx', 3 \halfcan') \otimes H^0 (\sx',
	(k - 3) \halfcan') \rightarrow H^0 (\sx',
	k \halfcan') \text{ if } k \geq 12 \text{ and } 3 \nmid k \\
	&H^0 (\sx', 7 \halfcan') \otimes H^0 (\sx',
	(k - 7) \halfcan') \rightarrow H^0 (\sx',
	k \halfcan') \text{ if } k \geq 6, k \not\equiv 0, 5
	\bmod 7
\end{align*}
